---
title: "Final Project P8106"
author: "Group 23"
date: "2022/5/6"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Library Load
```{r include=TRUE,warning=FALSE,message=FALSE}
library(tidyverse)
library(visdat)
library(caret)
library(arsenal)
library(missForest)
library(glmnet)
library(mlbench)
library(pROC)
library(pdp)
library(vip)
library(AppliedPredictiveModeling)
library(randomForest)
library(ranger)
library(gbm)
library(e1071)
library(kernlab)
```

## Background
Breast cancer is a disease in which malignant (cancer) cells form in the tissues of the breast. It is the second common cancer in women in the United States and is the second leading cause of cancer death in women. According to the American Cancer Society, incidence rates have increased by 0.5% per year recently. It imposes a severe public health problem for society for its substantial burden and disparities in treatment, care, and outcome. Early diagnosis often utilize a mammogram, an X-ray picture, to look for the signs of breast cancer and this requires regular screening since breast cancer takes years to be felt. Therefore, it’s important for women to take regular screening to be healthy or diagnosed with a benign tumor status before deterioration. 

## Motivation
Based on the past studies and reports, breast cancer has been a serious threat to people’s health for a long period and has the trend to be more prevailing. This cancer taking years to be felt even makes it difficult to be diagnosed and treated. X-ray mammogram as the most regular and powerful diagnosis method, this paper wants to study some potential sign related to tumor status from the features in the figure. Therefore, it is important for us to understand what are the risk factors associated with the breast cancer. According to the model result, we may predict whether one will develop a malignant tumor to provide a early diagnosis reference.

## Data Description
This dataset is designed to understand the possible predictor for type of Breast Cancer. It consists of 32 variables with 569 observations. The outcome of interest is a binary variable represents the type of breast cancer. The more specific information of the data can be found at [here](https://www.kaggle.com/datasets/yasserh/breast-cancer-dataset?resource=download).
```{r include=FALSE}
library(readr)
breast_cancer <- read_csv("breast-cancer.csv")
```






